### 2024-02-29 doc/15yrsChange.Rmd
Update 15yrsChange.Rmd
starting the second paragraph in the results (definitely still incomplete)

## Paragraph discussing broad trend of biomass stock decrease (Figure 2) & net change in biomass & differences among regions in the plot 
For the first time at the Front Royal ForestGEO site, C stocks have decreased since the last census (Figure 2). From 2018 to 2023, whole-plot C stocks have decreased from **"X to X"** Mg C/ha. There are different trends for the different regions of the plot. Both low nuisance regions show similar decreases in C stocks going from **"X to X"** and **"X to X"** Mg C/ha respectively. The magnitude of the decrease in the high der high nuisance area from 2018 to 2023 is greater, going from **"X to X"** Mg C/ha. C stock decrease **is related to/ is explained by** aboveground net woody production. In the first two census intervals, 2008 to 2013 and 2013 to 2018, there were positive C fluxes **VALUES?** and for the 2018 to 2023 interval there was a negative C flux of **VALUE Mg C/ha/year** (Figure 3a).

## Paragraph discussing constituent fluxes of net biomass change - across the whole plot & within regions

>>>>

## Paragraph discussing broad trend of biomass stock decrease (Figure 2) & net change in biomass & differences among regions in the plot 
For the first time at the Front Royal ForestGEO site, C stocks have decreased since the last census (Figure 2). From 2018 to 2023, whole-plot C stocks have decreased from **"X to X"** Mg C/ha. Both low nuisance regions show similar decreases in C stocks going from **"X to X"** and **"X to X"** Mg C/ha respectively. The magnitude of the C stock decrease in the high deer high nuisance area from 2018 to 2023 is larger, going from **"X to X"** Mg C/ha. C stock decrease **is related to/ is explained by** above ground net woody production. In the first two census intervals, 2008 to 2013 and 2013 to 2018, there were positive C fluxes **VALUES?** and for the 2018 to 2023 interval there was a negative C flux of **VALUE Mg C/ha/year** (Figure 3a).

## Paragraph discussing constituent fluxes of net biomass change - across the whole plot & within regions
The trend in net woody production can be explained by its constituent fluxes (Figure 3). Trends in woody mortality show that for the first two census intervals, the whole plot has lost **VALUE** and then **VALUE** Mg C/ha/year, increasing to a loss of **VALUE** Mg C/ha/year for the most recent census interval (Figure 3b). Woody productivity contributes positively to the flux, showing that the whole plot gained **VALUE** Mg C/ha/year in the first interval, **VALUE** Mg C/ha/year in the second, and **VALUE** Mg C/ha/year in the third (Figure 3c). Areas of low deer, low nuisance species were consistently the most productive ending at **VALUE** Mg C/ha/year in the interval 2018 to 2023, and areas of high deer, high nuisance species were the least productive at **VALUE** Mg C/ha/year in the interval 2018 to 2023.
